---
title: Course Project1 Making Plots
author: "AllenTsai"
date: "2015年8月7日"
output: html_document
---

### require libraries
  1. library(dplyr): easy to get the dataset for plot
  1. library(lubridate): easy to parse date object
### R scripts in ExData_Plotting1 repo

### CourseProject1.R: 
  1. predict required memory to read the whole file "household_power_consumption.txt"
  1. getData: 
     1. for performance issue, skip first 63000 rows and read 20000 rows only
     1. mutate data set to create weekday, year, month , mday, hour, minute, second
     1. filter dataset for whole day(2007/02/01, 2007/02/02), and 2007/02/03 00:00:00 [print Axis at Sat]
  1. setXAxis
     1. pickup datetime at 00:00:00 , to draw axis by weekday
  1. plotEnergySubMetering: plot energy sub metering
  
### plot1.R: create plot1
    histogram of global active power

### plot2.R: create plot2
    xyplot of global active power v.s. datetime

### plot3.R: create plot3
    xyplot Energy Sub metering plot v.s. datetime

### plot4.R: create plot4
    create 4 plots in one png

### How to create 4 plots
1. set workspace to the path with 5 R scripts and date set 
```{r}
#set environment
setwd("/Users/hadoop/ExData_Plotting1")
#create common script to read data, plot sub metering , draw axis with 
source("CourseProject1.R")

# define dataset filename
fileName="household_power_consumption.txt"
```

2. create plot1
```{r}
source("plot1.R")
```

3. create plot2
```{r}
#plot2
source("plot2.R")
```
4. create plot3
```{r}
#plot3
source("plot3.R")
```
5. create plot4
```{r}
#plot4
source("plot4.R")
```
