---
title: Course Project1 Making Plots
author: "AllenTsai"
date: "2015年8月7日"
output: html_document
---

### load required libraries
```{r}
# require library dplyr to mutate, filter data on 2007/02/01 and 2007/02/02
library(dplyr)
# require lubridate to get year, month, mday to filter data
library(lubridate)
```

### set workspace and define data set filename 
```{r}
# work directory with 5 R script and data set file insize
setwd("/Users/hadoop/ExData_Plotting1")

# define dataset filename
fileName= "household_power_consumption.txt"
```

### CourseProject1.R: 
  1. predict required memory to read the whole file "household_power_consumption.txt"
  1. getData function: 
     1. for performance issue, skip first 63000 rows and read 20000 rows only
     1. mutate data set to create weekday, year, month , mday, hour, minute, second
     1. filter dataset from 2007/02/01 to 2007/02/03(make plot and axis)
  1. setXAxis function
     1. filter datetime at 00:00:00, and makes axis by weekday
  1. plotEnergySubMetering function
     1. plot Sub_metering_1 v.s datetime
     1. lines Sub_metering_2 v.s datetime
     1. lines Sub_metering_3 v.s datetime
     1. create legend
```{r}
#define function for plotting
source("CourseProject1.R")
```

### plot1: histogram of global active power and save to png 
```{r}
source("plot1.R")
```

### plot2: xyplot of global active power v.s. datetime and save to png
```{r}
#plot2
source("plot2.R")
```

### plot3: xyplot Energy Sub metering plot v.s. datetime  and save to png 
```{r}
#plot3
source("plot3.R")
```

### plot4: create 4 plots in one plot  and save to png 
```{r}
#plot4
source("plot4.R")
```
